### 2013-11-21 PositionPaper/incremental.tex
no message

Given a requirement expressing a query and quality of service preferences : cost, provenance, reputation, time the system processes it according to the following steps:

>>>>

Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according to the following steps:
